DeepSphere: a graph-based spherical CNN

### 2020-02-14 main.tex
deanonymize

%\title{Which spherical CNN should you use?\\ DeepSphere V2}
\title{DeepSphere: a graph-based spherical CNN}
%\title{DeepSphere: an efficient graph-based spherical CNN}
%\title{DeepSphere, an efficient (& equivariant) graph-based spherical CNN}
\author{Michaël Defferrard, Martino Milani \& Frédérick Gusset \\
Institute of Electrical Engineering, EPFL, Lausanne, Switzerland \\
\texttt{\{michael.defferrard,martino.milani,frederick.gusset\}@epfl.ch}
\AND
Nathanaël Perraudin \\
Swiss Data Science Center (SDSC), Zurich, Switzerland \\
\texttt{nathanael.perraudin@sdsc.ethz.ch}
}

@@

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}

@@

\subsubsection*{Author Contributions}
Left blank for anonymity reason.
% If you'd like to, you may include a section for author contributions as is done
% in many journals. This is optional and at the discretion of the authors.

\subsubsection*{Acknowledgments}
Left blank for anonymity reason.

%We thank Pierre Vandergheynst for advices, and Andreas Loukas for having processed the GHCN data.
%We thank Taco Cohen for his inputs on the intriguing results of our comparison with \citet{cohen2019gauge}.
%We thank the anonymous reviewers for their constructive feedback.
%The following packages were used for computation and plotting: pygsp, numpy, tensorflow, scipy, etc.
%We used the Python Graph Signal Processing package (PyGSP) \citep{pygsp} for computations and plots.
%The Python Graph Signal Processing package (PyGSP) \citep{pygsp} was used to build graphs, compute the Laplacian and Fourier basis, and perform graph convolutions.

>>>>

%\title{Which spherical CNN should you use?\\ DeepSphere V2}
\title{DeepSphere: a graph-based spherical CNN}
%\title{DeepSphere: an efficient graph-based spherical CNN}
%\title{DeepSphere, an efficient (& equivariant) graph-based spherical CNN}
\author{Michaël Defferrard, Martino Milani \& Frédérick Gusset \\
École Polytechnique Fédérale de Lausanne (EPFL), Switzerland \\
\texttt{\{michael.defferrard,martino.milani,frederick.gusset\}@epfl.ch}
\AND
Nathanaël Perraudin \\
Swiss Data Science Center (SDSC), Switzerland \\
\texttt{nathanael.perraudin@sdsc.ethz.ch}
}

@@

\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}

@@

%\subsubsection*{Author Contributions}
%Left blank for anonymity reason.
% If you'd like to, you may include a section for author contributions as is done
% in many journals. This is optional and at the discretion of the authors.

\subsubsection*{Acknowledgments}

We thank Pierre Vandergheynst for advices.
%and Andreas Loukas for having processed the GHCN data.
We thank Taco Cohen for his inputs on the intriguing results of our comparison with \citet{cohen2019gauge}.
We thank the anonymous reviewers for their constructive feedback.
%The following software packages were used for computation and plotting: pygsp, scipy, numpy, tensorflow, etc.
%We used the Python Graph Signal Processing package (PyGSP) \citep{pygsp} for computations and plots.
